---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h1 {
  background-color: #f7fbfd;
  color: #9866C7;
  font-weight: bold;
  border-style: dotted;
  border-width: 4px;
}

h2 {
  color: #BF92E4;
  font-weight: medium;
  border-style: dotted;
  border-width: 3px;
}

body {
  font-family: Helvetica;
}

```

## Tracking My Music Usage 

```{r}
library(tidyverse)

# URL for the Google sheet published as a CSV
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSYKmCQXFj1VIlgXYgsuxby31AgK91k2jIbN0-D0n8xCuFq4-3Lxq9VzR3ZmeBx35Sge9D0xaJJ-pEo/pub?output=csv"

# Using the read_csv() function to read the data
# into a data frame named logged_data
logged_data <- read_csv(csv_file)

# printing out the latest_data data frame
latest_data <- logged_data %>%
  rename(time = 3,
         activity = 4, 
         music_duration = 5)

# bar plot with the activities 
ggplot(data = latest_data) +
  geom_bar(aes(x = activity),fill = "#9866C7")+
  labs(title = "Activities While Listening to Music",
       caption = "Source: Music Form by Sashika Ragavan",
       x = "Activities",
       y = "Count")

# bar plot with the duration of music  
ggplot(data = latest_data) +
  geom_bar(aes(x = music_duration),fill = "#BF92E4")+
  labs(title = "Duration of Music Listening Sessions",
       caption = "Source: Music Form by Sashika Ragavan",
       x = "Duration in Minutes",
       y = "Count ")

```

I created a form to observe and analyse my music listening habits over a period of 5 days. I gathered data on the time I listened to music, the activity I was doing and the duration. 

```{r}
total_hours <- sum(latest_data$music_duration/60) #number of hours 
```
The total number of hours I listened to music is `r total_hours`.

```{r}
maximum_min <- max(latest_data$music_duration) #max time listened 
```
The maximum number of minutes I listened to music is `r maximum_min`.

```{r}
minimum_min <- min(latest_data$music_duration) #min time listened 
```
The minimum number of minutes I listened to music is `r minimum_min`.
